---
title: "Initial Korean covid 19"
author: "Jaylen Johnson"
date: "3/30/2023"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
kRdata <- kRdata %>%
mutate(across(where(is.character), as.factor))

```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 2020
### This data was retrieved from a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
# Your Question - Is dying independent of sex?






## Graphical results - use ggplot commands to do this  


```{r}
barchartGC(~result + sex,data=kRdata)
barchartGC(~result + sex,data=kRdata, type="percent")

```
  
According to this graph there were more females that are alive than males meaning there were more males who died than females.  




  
## Numerical results

```{r}
table1 <- xtabs(~result + sex, data=kRdata)
rowPerc(table1)
colPerc(table1)
```


This data shows that 64% of males died due to covid while a much smaller 36% of women died.  Of those that did not die women still hold the higher % at 56 versus the males 44%.  



## Inferential results  

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

The data provided shows the total amount of people that lived or died due to the disease.  These numbers total 1832 females and 1411 males who lived meaning 25 females and 44 males died,  this means that ratio of men to women dyeing was 2:3.  


## Conclusions

In conclusion the disease has killed more men that women in Korea.  the first graph shows this information as well as the numerical data.  the inferential data provides a more detailed look giving more precise numbers on the total number of people form the data giving an odds ratio od 2:3 on female deaths to male deaths.  
